Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/results.tex
National Chokepoint Results

\Ben[inline]{We should answer the questions in the order we ask them. 1)
National Chokepoint potential and implications. 2) Comparison among nations. 3)
Evoluation over time.}

@@

\Ben[inline]{Include results here about general chokepoint potential,
currently}.

	To evaluate national chokepoint potentials of each of these nations we
plot from our \toolname{} generated results the

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{nationsCompare}
	\caption{The national chokepoint potentials of various nations in 2018. k is the
	percentage of paths used to calculate the national chokepoint potential.}\label{fig:nationsCompare}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesFree}
	\caption{The number of border ASes required for the US, France, Germany, and Great Britain to intercept 90\% of in-to-out paths over time.}\label{fig:nodesFree}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesCensor}
	\caption{The number of border ASes required for Russia, Egypt, Turkey, and China to intercept 90\% of in-to-out paths over time.}\label{fig:nodesCensor}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{multi}
	\caption{The capability for various nations to intercept in-to-out paths over multiple years \timerange. Each plot shows for a number of border ASes controlled (x-axis),
	what fraction of in-to-out paths are intercepted (y-axis). Years in blue are more recent, and years in red are further in the past.}\label{fig:multiTime}
\end{figure*}

We have chosen to detail the results of our national chokepoint potential
experiment for 8 nations due to
their histories of censorship practice. First we have chosen 4 nations known to
enact extensive Internet censorship policies. These nations are China, Turkey,
Egypt, and Russia. China has historically been the number one nation in regards
to Internet censorship \cite{censorshipSurvey}. Turkey has recently
dramatically increased its online censorship efforts, by blocking social media
accesses during turmoil and pressuring ISPs to block access to material chosen
by the Turkish government \cite{turkeyCensor}. The Internet of Egypt suffered
severe shutdowns during the Arab Spring of the early 2010s \cite{arabspring}.
The Russian government has passed surveillance laws requiring ISPs to allow the
Russian government access to user statistics \cite{censorshipGeography}. Next
we have chosen the nations of Germany, the United States, France, and the
United Kingdom because, while they have all conducted limited forms of Internet
censorship \cite{censorshipSurvey}, Internet access for these nations is
considered highly open.

>>>>

@@

	We have chosen to detail the results of our national chokepoint potential
experiment for 8 nations due to
their histories of censorship practice. First we have chosen 4 nations known to
enact extensive Internet censorship policies. These nations are China, Turkey,
Egypt, and Russia. China has historically been the number one nation in regards
to Internet censorship \cite{censorshipSurvey}. Turkey has recently
dramatically increased its online censorship efforts, by blocking social media
accesses during turmoil and pressuring ISPs to block access to material chosen
by the Turkish government \cite{turkeyCensor}. The Internet of Egypt suffered
severe shutdowns during the Arab Spring of the early 2010s \cite{arabspring}.
The Russian government has passed surveillance laws requiring ISPs to allow the
Russian government access to user statistics \cite{censorshipGeography}. Next
we have chosen the nations of Germany, the United States, France, and the
United Kingdom because, while they have all conducted limited forms of Internet
censorship \cite{censorshipSurvey}, Internet access for these nations is
considered somewhat open.

We present the national chokepoint potentials for these nations in 2018 with increasing
$f$ in \figurename \ref{fig:nationsCompare}. For each value of $f$, (on the x-axis),
the naitonal chokepoint potential, the inverse of the number of ASes needed to intercept
the fraction $f$ of paths is plotted. For all results we detail only the in-to-out results
because we find little difference between the results for in-to-out paths and out-to-in paths
for all our experiments.

\figurename \ref{fig:nationsCompare} shows us the diverse nature of national topologies. China is one
extreme example, where upto more than 80 percent of paths can be intercepted by a single AS, as indicated
by a NCP of 1.0. Other nations exhibiting strong chokepoints are Egypt, Turkey, and the United Kingdom. The
nations of the US, France, Germany, and Russia show considerably lower NCP for 2018.

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{nationsCompare}
	\caption{The national chokepoint potentials of various nations in 2018. k is the
	percentage of paths used to calculate the national chokepoint potential.}\label{fig:nationsCompare}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesFree}
	\caption{The number of border ASes required for the US, France, Germany, and Great Britain to intercept 90\% of in-to-out paths over time.}\label{fig:nodesFree}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesCensor}
	\caption{The number of border ASes required for Russia, Egypt, Turkey, and China to intercept 90\% of in-to-out paths over time.}\label{fig:nodesCensor}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{multi}
	\caption{The capability for various nations to intercept in-to-out paths over multiple years \timerange. Each plot shows for a number of border ASes controlled (x-axis),
	what fraction of in-to-out paths are intercepted (y-axis). Years in blue are more recent, and years in red are further in the past.}\label{fig:multiTime}
\end{figure*}
